Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
go biden go

For the US 2020 election between Biden and Trump, we forecast Biden to win the popular vote by 53.5% to 46.5% of the votes.

>>>>

For the US 2020 election between Biden and Trump, we forecast Biden to win the popular vote by 54% to 46% of the votes.

```{r}

overall_prop <- readRDS('../../processed_data/predictions.RDS')
biden <-sum(overall_prop$vote_weight)
trump <- 1 - biden

Candidates <- c("Biden", "Trump")
Percentage <- c(biden, trump)

data.frame(Candidates, Percentage) %>% 
  ggplot(aes(x = Candidates, 
             y= Percentage)) +
  geom_bar(stat = "identity")
```
